Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-12 doc/JFLA2022/paper.tex
add acknowledgment section

%\section{Acknowledgments}
%\label{sect:acks}

>>>>

\section{Acknowledgments}
\label{sect:acks}
We are grateful to the original authors and current maintainers of the Coq packages we use and depend on: José Grimm (Gaia), Russel O'Connor(Goedel), Matthieu Sozeau (Equations), the Mathematical Components team (ssreflect, algebra), Marc Lasson and Chantal Keller (Paramcoq), and the authors and maintainers
of \coq and its associated tools.
